30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
added text to browser based attacks

		\subsection{Browser based attacks}
		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}. By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\

@@

		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches. A similar system can be set up only using the HTML meta refresh tag. To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\

@@

Moving this system to a non peer-to-peer base is difficult. Dingledine et al. stated that this indeed is still an open problem. With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network. Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.

		\subsection{Incentives in decentralized systems}
		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate. There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor. If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified. In other words the incentive data has to be accurate and reliable. Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\

		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network. The first thing that is described is the so called \emph{Warm-glow Model}. In this model determines the percentage of free-rides based on the probabilistic population distribution. If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\

>>>>

		\subsection{Browser based attacks}
		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}. By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\

@@

		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches. A similar system can be set up only using the HTML meta refresh tag. To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666. Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.\\

@@

Moving this system to a non peer-to-peer base is difficult. Dingledine et al. stated that this indeed is still an open problem. With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there may be a lot of malicious nodes in the network. Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.

		\subsection{Incentives in decentralized systems}
		As described in section \ref{ss:tor_disadvantages}, most users are using more bandwidth than that they donate. There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor. If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified. In other words the incentive data has to be accurate and reliable. Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\

		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a decentralized peer-to-peer network. The first thing that is described is the so called \emph{Warm-glow Model}. In this model determines the percentage of free-rides based on the probabilistic population distribution. If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\
